# Reproducible Research: Peer Assessment 1
## Loading and preprocessing the data
In the first step, we should load the data and drop missing values 
(we assume that there is "activity.csv"
in working directory):

```{r, echo = TRUE}
    library(lattice)
    raw_data <- read.csv("activity.csv")
    data <- raw_data[complete.cases(raw_data), ]
    mean_per_interval <- tapply(data[["steps"]], data[["interval"]], mean)
```


## What is mean total number of steps taken per day?
Make a histogram of the total number of steps taken each day:

```{r, echo=TRUE}
hist(tapply(data[["steps"]], data$date, sum),  
     xlab = "Total number of steps", 
     main = "Histogram of number of steps")
    
```

Let calculate mean and median values
```{r, echo = TRUE}
    tapply(data[["steps"]], data$date, mean)
    tapply(data[["steps"]], data$date, median)
```

## What is the average daily activity pattern?
Make a time series plot (i.e. type = "l") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
```{r, echo = TRUE}
    plot(tapply(data[["steps"]], data[["interval"]], mean), type = "l")
```
Find a maximum
```{r, echo=TRUE}
    max(unlist(split(data[["steps"]], data[["interval"]])))
```

## Imputing missing values
Number of missing values:
```{r, echo = TRUE}
    len <- nrow(raw_data)
    len - sum(complete.cases(raw_data))
```

Put in place of missing values mean of time interval:
```{r, echo = TRUE}
    update_data <- raw_data
    for (i in 1 : length(update_data[["steps"]]))
        if (is.na(update_data[i, "steps"]))
            update_data[i, "steps"] <- 
                    mean_per_interval[as.character(data[i, "interval"])]
```

There is a beginig of a new dataset:
```{r, echo = TRUE}
    head(update_data)
```

Make a new histogram
```{r, echo=TRUE}
hist(tapply(update_data[["steps"]], update_data$date, sum),  
     xlab = "Total number of steps", 
     main = "Histogram of number of steps")
    
```

Let calculate mean and median values
```{r, echo = TRUE}
    tapply(update_data[["steps"]], update_data$date, mean)
    tapply(update_data[["steps"]], update_data$date, median)
```


## Are there differences in activity patterns between weekdays and weekends?
```{r, echo = TRUE}
    for (i in 1 : length(update_data$date))
        update_data[i, "new_date"] <- 
            (as.POSIXlt(update_data[i, "date"])$wday %% 6 == 0)

    new_mean <- tapply(update_data[["steps"]], update_data$date, mean)
    #class(new_mean)
    #head(new_mean)
    xyplot(new_mean ~ 1:length(new_mean) | update_data$new_date, 
           type = "l")
```


